Home Nighttime Cough Monitoring

### 2025-01-29 Lilah Melzer/cough_monitor_analysis.qmd
CFQ-R mostly done, check with Edith and Lilah

```{r}
# CFQ-R Caregivers 6-13
cfqr_6_13 <- df %>%
  filter(redcap_repeat_instrument == "CFQ-R Caregivers 6-13") %>%
  select(sid, Diagnosis, cfqr_caregivers_613_timestamp:cfqr_caregivers_613_complete)
```

>>>>

```{r}
# CFQ-R Caregivers 6-13
# SAS code
# if nmiss (phys1, phys2, phys3, phys4, phys5, phys6) <= 3 then
# physical = (mean (phys1, phys2, phys3, phys4, phys5, phys6)-1)/3*100;
#
# if nmiss (emot7, emot8, emot9, emot10, emot11, emot12, emot13, emot14) <= 4 then
# emotion = (mean (emot7, emot8, emot9, emot10, emot11, emot12, emot13, emot14)-1)/3*100;
#
# if nmiss (social20, social21, social22, social23, social24, social25, social26) <= 3 then
# social = (mean (social20, social21, social22, social23, social24, social25, social26)-1)/3*100;
#
# if nmiss (eat15, eat17, eat19) <= 1 then
# eat = (mean(eat15, eat17, eat19)-1)/3*100;
#
# if nmiss (body27, body28, body29) <= 1 then
# body = (mean(body27, body28, body29)-1)/3*100;
#
# if nmiss (treat16, treat18, treat30) <= 1 then
# treat = (mean (treat16, treat18, treat30)-1)/3*100;
#
# if nmiss (resp31, resp32, resp33, resp34) <= 2 then
# respirat = (mean (resp31, resp32, resp33, resp34)-1)/3*100;
#
# if nmiss (digest35) = 0 then
# digest = (mean (digest35)-1)/3*100;

cfqr_6_13 <- df %>%
  filter(redcap_repeat_instrument == "CFQ-R Caregivers 6-13") %>%
  select(
    sid, Diagnosis, cfqr_caregivers_613_timestamp:cfqr_caregivers_613_complete
  )

cfqr_6_13$cfqr_physical <- apply(
  data.matrix(cfqr_6_13[, paste0("cfq_r_p_", 1:5)]), 1, function(r) {
    (mean(r) - 1) / 3 * 100
  }
)
cfqr_6_13$cfqr_emotion <- apply(
  data.matrix(cfqr_6_13[, paste0("cfq_r_p_", 6:13)]), 1, function(r) {
    (mean(r) - 1) / 3 * 100
  }
)
